---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stocked

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/davisadamw/stocked.svg?branch=master)](https://travis-ci.org/davisadamw/stocked)
<!-- badges: end -->

The goal of stocked is to make it easier to keep all the code straight for weird iterative bass models like what we're using for the market share tool.

## Installation

And the development version from [GitHub](https://github.com/davisadamw/stocked) with:

``` r
# install.packages("devtools")
devtools::install_github("davisadamw/stocked")
```
## Example

This is a basic example of how to use this package's functions to calculate the slope of a bass curve at a given level of market penetration:

```{r example}
library(stocked)
bass(M = 0.5, p = 0.05, q = 0.4)
```

## Bug Notes:

The `prep_data()` function argument `bump_ml` currently throws an error if left as default (`FALSE`). Recommend setting it to true and manually ensuring starting value / total is not higher than allowed if you want to mimic non-bumped ml behavior.


